---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

__5.1 (Exploring percentages of small classes).__ The variable Pct.20 in the college dataset contains the percentage of "small classes" (defined as 20 or fewer students) in the National Universities. <br>
__a.__ Construct a dotplot of the small-class percentages using the stripchart function. To see the density of points, it is helpful to use either the method=stack or method=jitter arguments. What is the shape of this data? <br>
__b.__ There is a single school with an unusually large small-class percentage. Use the identify function to find the name of this unusual school.<br>
__c.__ Find the median small-class percentage and draw a vertical line (using the abline function) on the dotplot at the location of the median.<br>


```{r}
dat = read.table("college.txt", header=TRUE, sep="\t")
college = subset(dat, complete.cases(dat))
stripchart(college$Pct.20, method="stack", pch= 19, xlab="Small-class percentages")
```



```{r }
stripchart(college$Pct.20 ~ college$Tier, method="stack", pch= 19, xlab="Small-class percentages", ylab = "Tier")
identify(college$Retention, college$Tier, n=1, labels=college$School)
```

```{r}
med = median(college$Pct.20)
stripchart(college$Pct.20, method="stack", pch= 19, xlab="Small-class percentages")
abline(v = med, col = "red")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
